Packaging research artifacts with RO-Crate

### 2021-05-06 latex/ro-crate.tex
formal definitions are in appendix
appendix moved down
Updates from Overleaf

\DeclareGraphicsExtensions{.png,.pdf}
\graphicspath{../content/images/}
\usepackage[citations,fencedCode,footnotes,hybrid,pipeTables,smartEllipses,tableCaptions,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

@@

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
    Extension={.otf},
    Path=./STIX2fonts/,
    Scale=1
]
\setmainfont{STIX2Text}[
    Extension={.otf},
    Path=./STIX2fonts/,
    UprightFont={*-Regular},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic}
]
% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
    Extension={.ttf},
    Path=./ttf-iosevka-slab-6.1.3/,
    Scale=MatchLowercase,
    UprightFont={*-light},
    ItalicFont={*-lightitalic}
]

@@

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\author[B]{\inits{P.G.}\fnms{Paul} \snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}

@@

% Every *.md file in content/ in order, except 00, 90
\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/80.formal-definition.md}
% TODO: Recode formal definition to LaTeX math mode?
%\input{../content/80.formal-definition.tex}

%%%%%%%%%%% The bibliography starts:

\nocite{*} 
% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{ios1}           % Style BST file.
\bibliography{ro-crate}        % Bibliography file (usually '*.bib')

>>>>

\DeclareGraphicsExtensions{.pdf,.png,.svg}
\graphicspath{../content/images/}
\usepackage[citations,fencedCode,footnotes,hybrid,pipeTables,smartEllipses,tableCaptions,underscores]{markdown}
\def\markdownOptionOutputDir{../output}

@@

% Welcome to the 2000s with UNICODE fonts!
% Adapted from
% https://www.overleaf.com/learn/latex/Articles%2FOpenType-based_math_typesetting:_An_introduction_to_the_STIX2_OpenType_fonts
\setmathfont{STIX2Math}[
    Extension={.otf},
    Path=./STIX2fonts/,
    Scale=1
]
\setmainfont{STIX2Text}[
    Extension={.otf},
    Path=./STIX2fonts/,
    UprightFont={*-Regular},
    BoldFont={*-Bold},
    ItalicFont={*-Italic},
    BoldItalicFont={*-BoldItalic}
]

% https://typeof.net/Iosevka/ mono font has 
% all; the logic symbols we need
\setmonofont{iosevka-slab}[
    Extension={.ttf},
    Path=./ttf-iosevka-slab-6.1.3/,
    Scale=MatchLowercase,
    UprightFont={*-light},
    ItalicFont={*-lightitalic}
]

@@

% Two or more authors:
\author[A,B]{\fnms{Stian} \snm{Soiland-Reyes}\ead[label=e1]{soiland-reyes@manchester.ac.uk}\ead[label=o1,orcid]{0000-0001-9842-9718}%
\thanks{Corresponding author. \printead{e1}.}},
\author[C]{\inits{P.S.}\fnms{Peter} \snm{Sefton}\ead[label=e2]{Peter.Sefton@uts.edu.au}\ead[label=o2,orcid]{0000-0002-3545-944X}},
\author[D]{RO-Crate Community},
\author[A]{\inits{C.G.}\fnms{Carole} \snm{Goble}\ead[label=e3]{carole.goble@manchester.ac.uk}\ead[label=o3,orcid]{0000-0003-1219-2137}},
\author[B]{\inits{P.G.}\fnms{Paul} 
\snm{Groth}\ead[label=e3]{p.t.groth@uva.nl}\ead[label=o3,orcid]{0000-0003-0183-6910}}
\address[A]{Computer Science, \orgname{The University of Manchester},
\cny{UK}\printead[presep={\\}]{e1,o1}}
\address[B]{Informatics Institute, \orgname{University of Amsterdam},
\cny{The Netherlands}\printead[presep={\\}]{e2,o2}}
\address[C]{Faculty of Science, \orgname{University Technology Sydney},
\cny{Australia}\printead[presep={\\}]{e3,o3}}
\address[D]{\url{https://www.researchobject.org/ro-crate/community} (see appendix B)}

@@

% Every *.md file in content/ in order, except 00, 90
\markdownInput{../content/10.background.md}
\markdownInput{../content/20.rocrate.md}
\markdownInput{../content/21.conceptual.md}
\markdownInput{../content/22.implementation.md}
\markdownInput{../content/23.community.md}
\markdownInput{../content/30.tooling.md}
\markdownInput{../content/40.inuse.md}
\markdownInput{../content/41.workflows.md}
\markdownInput{../content/42.regulatory.md}
\markdownInput{../content/43.culturalheritage.md}
\markdownInput{../content/50.relatedwork.md}
\markdownInput{../content/60.conclusion.md}
\markdownInput{../content/70.acknowledgements.md}

%%%%%%%%%%% The bibliography starts:
\nocite{*} 
\bibliographystyle{ios1}
\bibliography{ro-crate}

%%%% Appendix

\appendix
\markdownInput{../content/80.formal-definition.md}
% TODO: Recode formal definition to LaTeX math mode?
%\input{../content/80.formal-definition.tex}
\markdownInput{../content/89.community.md}
